I need a title

### 2018-01-07 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

\begin{document}
\maketitle
\begin{abstract}
Interviews are the most common technique in requirements elicitation.
However, the presence of tacit knowledge have an important influence on
interviews success. In this paper, we describe a tacit knowledge
classification. Then we make use of a theoretical framework and examples
to detect and minimize the effects of tacit knowledge. Finally, we
analyze how likely is to have a sucessful elicitation interviews based
on the tacit knowledge classification.

@@

Requirements engineering is the subset of systems engineering concerned
with discovering, developing, tracing, analyzing, qualifying,
communicating and managing requirements that define the system at
succesive levels of abstraction {[}1{]}. The first step of requirements
engineering is requirements elicitation which is defined as the process
of finding and formulation requirements {[}2{]}, and this process has
many barriers due to stakeholders are not able to express their needs,
explain what they do and why, conflicting demands, or new demands once
other are met, just to mention some examples.

One of the most used techiques to elict requirements is open interviews,
and also is considered the most effective way to transfer domain
knowledge {[}3{]}. However, the success of interviews depends on mainly
two factors, analyst set of interviewing skills and stakeholders domain
knowledge; nonetheless, statistically analyst domain knowledge is
important but not as relevant as the other two{[}4{]}. Therefore,
analyst should make use of tools and techniques to detect and elicit
tacit knowledge form stakeholders. Tacit knowledge is in requirements
engineering is defined as the knowledge that a stakeholders has, but
does not pass to the requirements analyst {[}5{]}.

In this paper we describe a classification of tacit knowledge in
elicitation interviews based on {[}6{]}. Then we apply the theoretical
framework described in {[}3{]} in examples to show how to deal with
tacit knowledge. The examples were selected in order to match the each
scenario of the classification. Finally, we use the result from {[}4{]}
to identify in which scenario is most likely to perform a succesful
interview.

@@

Attacks: A2 attacks B1, and viceversa.

@@

The attacks: A1 attacks B2, and viceversa

@@

One of the customers wants to develop an app to manage medical-related
reservation in Tuscani. The costumer mentioned that the \emph{current
reservation system, based on phone calls, was centralised}. During the
interview, the customer said that \emph{depending on where the
examination/visit will be, the patient has to call Nottola or Siena}.
The analyst could not understand how this realization was possible since
it means the reservation system is not centralized. Therefore the
analyst asked for clarification and the stakeholder couldn't give any
acceptable answer.

@@

The attacks: A1 attacks B3, and viceversa

@@

In the last section we present how to use a theoretical framework based
on arguments and attacks to addresed the different levels of tacit
knowledge. In this section we will compare in which scenario of tacit
knowledge the elicitation interview would be more effective based on
Aranda et al.~work {[}4{]} about the effect of domain knowledge on
elicitation process.\\
Effectiveness is described in {[}4{]} as the total percentage of problem
domain elements identified compared to a benchmark. However, since we
have no accesse to any requirement data, we will use the conclusions of
{[}4{]} to compare the different scenarios of tacit knowledge (known
unknowns, unknown knowns and unknowns unknowns).

The works presented in {[}4{]} concludes that: (1)analyst's domain
knowledge(ADK) has small but statisticall significant effect on the
effectiveness, (2)stakeholders' domain knowledge(SDK) has a big positive
and significant influence and (3)analyst's interviewing skill and
general training in requirement activities have also a big positive and
significant influence. In this paper, we will focus only in comparing
based on the domain knowledge holder since that knowledge can be
measured.

@@

We can observed in Table 1 that it is more likely to be effective in the
scenario of \emph{unknown knowns} because the stakeholders' domain
knowledge have more influence than analyst's domain knowledge. On the
other hand, the analyst's interviewing skills will have different
approaches in the case of \emph{known unknowns} and \emph{unknown
knowns}. In the first case, the interview will be more focused on
challenging assumptions and implications, and in the latter case on
spoting glympses of stakeholders' hidden knowledge.

@@

Elicitation interviews is not an easy task. Like in any intensive oral
communication there are missunderstandings related to tacit knowledge.
In our work we focus on analysing the different levels of how tacit
knowledge{[}6{]} would affect the effectiveness of elicitation
interviews. Moreover, we use the theoretical framework described in
{[}3{]} to indentify and manage tacit knowledge during interviews. And
finally, we analyze based on the results of {[}4{]} in which scenario of
tacit knowledge it is more likely to have a sucessful elictation
interview.

>>>>

\begin{document}
\maketitle
\begin{abstract}
Interviews are the most common technique in requirements elicitation.
However, the presence of tacit knowledge have an important influence on
interviews success. In this paper, we describe a tacit knowledge
classification. Then, we make use, with examples, of a theoretical
framework to detect and minimize the effects of tacit knowledge.
Finally, we analyze how likely is to have a successful elicitation
interviews based on the tacit knowledge classification.

@@

Requirements engineering is the subset of systems engineering concerned
with discovering, developing, tracing, analyzing, qualifying,
communicating and managing requirements that define the system at
successive levels of abstraction {[}1{]}. The first step of requirements
engineering is requirements elicitation which is defined as the process
of finding and formulation requirements {[}2{]}, and this process has
many barriers due to stakeholders are not able to express their needs,
explain what they do and why, conflicting demands, or new demands once
other are met, just to mention some examples.

One of the most used techniques to elicit requirements is open
interviews, and also is considered the most effective way to transfer
domain knowledge {[}3{]}. However, the success of interviews depends on
mainly two factors, analyst set of interviewing skills and stakeholders
domain knowledge; nonetheless, statistically analyst domain knowledge is
important but not as relevant as the other two{[}4{]}. Therefore,
analyst should make use of tools and techniques to detect and elicit
tacit knowledge form stakeholders. Tacit knowledge is in requirements
engineering is defined as the knowledge that a stakeholders has, but
does not pass to the requirements analyst {[}5{]}.

In this paper we describe a classification of tacit knowledge in
elicitation interviews based on {[}6{]}. Then we apply the theoretical
framework described in {[}3{]} in examples to show how to deal with
tacit knowledge. The examples were selected in order to match the each
scenario of the classification. Finally, we use the result from {[}4{]}
to identify in which scenario is most likely to perform a successful
interview.

@@

Attacks: A2 attacks B1, and vice versa.

@@

The attacks: A1 attacks B2, and vice versa

@@

One of the customers wants to develop an app to manage medical-related
reservation in Tuscani. The costumer mentioned that the \emph{current
reservation system, based on phone calls, was centralized}. During the
interview, the customer said that \emph{depending on where the
examination/visit will be, the patient has to call Nottola or Siena}.
The analyst could not understand how this realization was possible since
it means the reservation system is not centralized. Therefore the
analyst asked for clarification and the stakeholder couldn't give any
acceptable answer.

@@

The attacks: A1 attacks B3, and vice versa

@@

In the last section we present how to use a theoretical framework based
on arguments and attacks to addressed the different levels of tacit
knowledge. In this section we will compare in which scenario of tacit
knowledge the elicitation interview would be more effective based on
Aranda et al.~work {[}4{]} about the effect of domain knowledge on
elicitation process.\\
Effectiveness is described in {[}4{]} as the total percentage of problem
domain elements identified compared to a benchmark. However, since we
have no access to any requirement data, we will use the conclusions of
{[}4{]} to compare the different scenarios of tacit knowledge (known
unknowns, unknown knowns and unknowns unknowns).

The works presented in {[}4{]} concludes that: (1)analyst's domain
knowledge(ADK) has small but statistically significant effect on the
effectiveness, (2)stakeholders' domain knowledge(SDK) has a big positive
and significant influence and (3)analyst's interviewing skill and
general training in requirement activities have also a big positive and
significant influence. In this paper, we will focus only in comparing
based on the domain knowledge holder since that knowledge can be
measured.

@@

We can observed in Table 1 that it is more likely to be effective in the
scenario of \emph{unknown knowns} because the stakeholders' domain
knowledge have more influence than analyst's domain knowledge. On the
other hand, the analyst's interviewing skills will have different
approaches in the case of \emph{known unknowns} and \emph{unknown
knowns}. In the first case, the interview will be more focused on
challenging assumptions and implications, and in the latter case on
spotting glimpses of stakeholders' hidden knowledge.

@@

Elicitation interviews is not an easy task. Like in any intensive oral
communication there are misunderstandings related to tacit knowledge. In
our work we focus on analyzing the different levels of how tacit
knowledge{[}6{]} would affect the effectiveness of elicitation
interviews. Moreover, we use the theoretical framework described in
{[}3{]} to identify and manage tacit knowledge during interviews. And
finally, we analyze based on the results of {[}4{]} in which scenario of
tacit knowledge it is more likely to have a successful elicitation
interview.
